Data Exploration

### 2019-01-16 src/data_exploration.Rmd
addition of some individual box plots

temperature
```{r}
par(mfrow=c(1,2))
boxplot(presence$temp_depth, main = "Temp at Depth (Various)", ylab = "Kelvin")
boxplot(presence$temp_surface, main = "Temp at Surface", ylab = "Kelvin")
dev.copy(png, "../output/env/simple_plots/temperature_boxplot.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

>>>>

individual plots of each variable 
```{r}
par(mfrow=c(1,2))
boxplot(presence$temp_depth, main = "Temperature at Depth (Various)", ylab = "Kelvin")
boxplot(presence$temp_surface, main = "Temperature at Surface", ylab = "Kelvin")
dev.copy(png, "../output/env/simple_plots/temp_boxplot.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

par(mfrow=c(1,2))
boxplot(presence$salinity_depth, main = "Salinity at Depth (Various)", ylab = "PSU")
boxplot(presence$salinity_surface, main = "Salinity at Surface", ylab = "PSU")
dev.copy(png, "../output/env/simple_plots/salinity_boxplot.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

par(mfrow=c(1,2))
boxplot(presence$o2_depth, main = "O2 at Depth (Various)", ylab = "mmol.m-3")
boxplot(presence$o2_surface, main = "O2 at Surface", ylab = "mmol.m-3")
dev.copy(png, "../output/env/simple_plots/o2_boxplot.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

par(mfrow=c(1,2))
boxplot(presence$chl_depth, main = "Chlorphyll at Depth (Various)", ylab = "mmol.m-3")
boxplot(presence$chl_surface, main = "Chlorphyll at Surface", ylab = "mmol.m-3")
dev.copy(png, "../output/env/simple_plots/chl_boxplot.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

par(mfrow=c(1,2))
boxplot(presence$mlp_surface, main = "Density Mixed Layer Thickness", ylab = "meters")
boxplot(presence$ssh_surface, main = "Sea Surface Height", ylab = "meters")
dev.copy(png, "../output/env/simple_plots/mlp_ssh_boxplot.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```
